Web Service Community \\ Learning

### 2014-06-12 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

In this paper, we have implemented [OurMethodName] in which we initially train our services in different possible communities and let them experiment and check the outcome of different scenarios. Based on the trained results these services can be utilized with efficient methods of foreseeing how each of their decisions would impact their long term and short term goals, therefore opting for best decision available. Having a set of web services with pre-defined set of features, we let web services evaluate performance collaborating with a small subset of other web services. Each web service individually will be utilized with knowledge of collaborating with web services having different set of feature values. By deploying a linear distant function, the web services will be able to predict the outcome of collaborating with different web services which may not have been collaborated in during training process.

- We want to give full distributed control to web services as autonomous agents and distribute the task of community management among all web services and let them decide how to maximize their efficiency and join and create communities.
- Let agents train and learn long term expectations of each action and group they can join with
- Web services cannot find the optimal solution in big space problem of many web services
- Add rationalism and less vague decisions

>>>>

In this paper, we have implemented [OurMethodName] in which we initially train our services in different possible communities and let them experiment and check the outcome of different scenarios. Based on the trained results these services can be utilized with efficient methods of foreseeing how each of their decisions would impact their long term and short term goals, therefore opting for best decision available.

Web services have different set of features. These features are derived from quality metrics of web services. The values of these features influences the utility of the web services and when collaborating with our web services, these set of features determines the utility and performance of community. Having a set of web services with pre-defined set of features, we let web services evaluate performance of collaboration with a small subset of other web services. Keeping a history of the output estimate of this collaboration, each web service individually will be utilized with knowledge of collaboration with web services having different set of feature values. We keep this history and train web services so they can deduct how they would perform collabration with new web services having new set of feature values. By deploying a linear distant function, the web services will be able to predict the outcome of collaboration with different web services which may not have been collaborated in during training process.

%- We want to give full distributed control to web services as autonomous agents and distribute the task of community management among all web services and let them decide how to maximize their efficiency and join and create communities.
%- Let agents train and learn long term expectations of each action and group they can join with
%- Web services cannot find the optimal solution in big space problem of many web services
%- Add rationalism and less vague decisions
